Figures

### 2019-05-16 figures/06_lulc_buffer_demo.Rmd
add cdl vs nlcd map

llid <- dt$lagoslakeid[2]
ll_pnt <- st_coordinates(
  st_transform(
    query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", llid), 4326))
ll_lake <- st_transform(
  query_gis("LAGOS_NE_All_Lakes_4ha", "lagoslakeid", llid), 4326)
network <- extract_network(lon = ll_pnt[1], 
                                   lat = ll_pnt[2], 
                                   maxsteps = Inf, 
                           buffer_dist = units::as_units(5, "km"),
                           quiet = TRUE)
network <- network[unlist(lapply(
  st_intersects(network, st_transform(ll_lake, st_crs(network))), 
  function(x) length(x) == 0)),]

network_buffer <- st_buffer(network, 100)
nlcd           <- get_nlcd(template = as_Spatial(st_as_sfc(st_bbox(network_buffer))), 
                 label = llid)
network_buffer <- st_transform(network_buffer, projection(nlcd))

@@

```{r cdl_viewport, fig.height=5}
library(raster)
library(dplyr)

cdl_key <- read.csv("../data/cdl/cdl_key.csv", stringsAsFactors = FALSE)

r  <- raster::raster("../data/cdl/2745.tif")

@@

color_key <- data.frame(category = test2$category, 
                         color_cat = c("ag", "ag", "ag", "ag", "ag", "ag", 
                                       "water", "dev", "forest"),
                         color = c(
                           RColorBrewer::brewer.pal(6, "YlOrBr"), 
                           "#9ecae1", "#000000", "#2ca25f"),
                        stringsAsFactors = FALSE)
color_key <- arrange(color_key, color_cat)

@@

>>>>

llid <- 2745
ll_pnt <- st_coordinates(
  st_transform(
    query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", llid), 4326))
ll_lake <- st_transform(
  query_gis("LAGOS_NE_All_Lakes_4ha", "lagoslakeid", llid), 4326)
network <- extract_network(lon = ll_pnt[1], 
                                   lat = ll_pnt[2], 
                                   maxsteps = Inf, 
                           buffer_dist = units::as_units(5, "km"),
                           quiet = TRUE)
network <- network[unlist(lapply(
  st_intersects(network, st_transform(ll_lake, st_crs(network))), 
  function(x) length(x) == 0)),]
iws  <- query_gis("IWS", "lagoslakeid", llid)

network_buffer <- st_buffer(network, 100)
nlcd           <- get_nlcd(template = as_Spatial(st_as_sfc(st_bbox(iws))), 
                 label = llid)
# mapview(nlcd) + mapview(iws)
network_buffer <- st_transform(network_buffer, projection(nlcd))

@@

```{r cdl_viewport, fig.height=5}
# pull cdl lulc
cdl_key <- read.csv("../data/cdl/cdl_key.csv", stringsAsFactors = FALSE)
r  <- raster::raster("../data/cdl/2745.tif")

@@

color_key <- data.frame(category = test2$category, 
                         color_cat = c("ag", "ag", "ag", "ag", "ag", "pasture", 
                                       "water", "dev", "forest"),
                         color = c(
                           RColorBrewer::brewer.pal(5, "YlOrBr"), "#DBD83D",
                           "#9ecae1", "#000000", "#2ca25f"),
                        stringsAsFactors = FALSE)
color_key <- arrange(color_key, color_cat)

@@

```{r cdl_vs_nlcd}
# mask nlcd lulc

test <- raster::mask(nlcd, iws) %>% 
  as.data.frame(xy = TRUE) %>%
  dplyr::select(x, y, contains("Value"))
test <- test[test[,3] %in% c(81, 82),]
test[,3] <- factor(test[,3])
names(test)[3] <- "value"
test <- test %>%
  drop_na("value")
cols <- dplyr::filter(pal_nlcd(), code %in% unique(test[,3]))

# codes 81 = pasture; 82 = row_crop

g_nlcd <- ggplot() + 
  geom_raster(data = test, aes(x = x, y = y, fill = value)) +
  scale_fill_manual(values = cols$color, labels = cols$description) +
  geom_sf(data = iws, alpha = 0) +
  coord_sf(datum = NA) + 
  theme_void() + 
  theme(legend.position = 0)

g_cdl <- ggplot() + 
  geom_raster(data = dplyr::filter(cdl_df, as.character(category) %in% 
                                     c("corn", "soybeans", "pasture")), 
              aes(x = x, y = y, fill = category)) +
  scale_fill_manual(values = setNames(color_key$color, 
                                      color_key$category)) +
  geom_sf(data = iws, alpha = 0) +
  geom_sf(data = network) +
  geom_sf(data = ll_lake) +
  coord_sf(datum = NA) + 
  theme_void()

cowplot::plot_grid(g_nlcd + ggtitle("NLCD (2011)"), 
                   g_cdl + ggtitle("CDL (2010)"), 
                   rel_widths = c(0.75, 1))
```
